---
title: "Mapping Basics Exercise"
author: "Devon Mastin"
output: 
  html_document:
    toc: yes
    toc_flota: TRUE
    collapsed: no
    smooth_scroll: yes
    df_print: paged
  editor_options:
    chunk_output_type: inline
    mode: gfm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
pacman::p_load("leaflet", "sf", "tidyverse", "sp", "mapview", "maps", "mapdata")
```

The dataset that I am using for these maps comes from meuse dataset in the sp package. It contains data on heavy metals measured in the top soil along the Meuse River in the Netherlands. 

## Simple Map

This is a static map of the Netherlands and includes a visual of the Meuse River.
```{r}
map("world2", "Netherlands", col = 4, fill = TRUE)
lines(c(-4.05, -5.75, -6.05, -6.60), c(51.55, 51.52, 51.35, 51.12), col = "blue", lwd = 2)
title("Map of the Netherlands with Meuse River")
```


## Interactive Map

This map uses the mapview package to create an interactive map of the meuse river region with included measurements from each data point.

```{r}
data("meuse")
coordinates(meuse) <- ~x + y
proj4string(meuse) <- CRS("+init=epsg:28992")
mapview(meuse)
```


